\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.2in, headheight=14.5pt]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fancyhdr}

% Brand Colors
\definecolor{navy}{HTML}{002B66}
\definecolor{royalblue}{HTML}{2563EB}
\definecolor{amber}{HTML}{B45309}
\definecolor{text}{HTML}{0F172A}
\definecolor{textlight}{HTML}{475569}

\hypersetup{
    colorlinks=true,
    linkcolor=royalblue,
    filecolor=royalblue,      
    urlcolor=royalblue,
    pdftitle={Welcome to StatBridge Studio - Survey / Thesis Analysis},
    pdfpagemode=FullScreen,
}

% Page styling
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{textlight}{\footnotesize StatBridge Studio}}
\lhead{\textcolor{textlight}{\footnotesize Hotmart Deliverable}}
\rfoot{\textcolor{textlight}{\footnotesize \thepage}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

% Header Block
\begin{center}
    {\Huge \bfseries \textcolor{navy}{StatBridge Studio}} \\[0.25em]
    {\small \bfseries \textcolor{amber}{STATISTICAL \& RESEARCH SUPPORT}} \\
    \rule{\linewidth}{1.5pt}
\end{center}

\vspace{2em}

{\LARGE \bfseries \textcolor{navy}{Welcome to your Survey / Thesis Analysis!}}

Let's get your dataset structured and analyzed. To start cleaning your files, formulating frequency reports, and executing your hypothesis tests, please follow these steps.

\vspace{1.5em}

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.8pt}}
\vspace{-0.5em}
\begin{center}
\begin{minipage}{0.95\textwidth}
    {\large \bfseries \textcolor{navy}{Next Steps for Your Project}}
    \begin{enumerate}[label=\textbf{\color{royalblue}\arabic*.}, leftmargin=1.5em]
        \item \textbf{Prepare your dataset \& questionnaire} \\
        Gather your data files (Excel, CSV, Google Sheets, or SPSS formats) and your survey questionnaire. Ensure you outline your research goals and hypothesis statements clearly.
        
        \item \textbf{Send the files by email} \\
        Send an email to \href{mailto:hello@statbridgestudio.com}{\texttt{hello@statbridgestudio.com}} with the subject line: \\
        \textbf{[StatBridge] Files for Survey/Thesis Analysis - [Your Name]}
        
        \item \textbf{Methodology \& Delivery} \\
        I will confirm receipt within 24 hours. Messy labels will be cleaned, frequency and descriptive parameters evaluated, and hypothesis models executed. You will receive report-ready tables, descriptive charts, and summary notes to write your results.
    \end{enumerate}
\end{minipage}
\end{center}
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.8pt}}

\vspace{3em}

\begin{center}
    \textcolor{textlight}{Need help? Contact me directly at} \href{mailto:hello@statbridgestudio.com}{\texttt{hello@statbridgestudio.com}} \\[1.5em]
    \rule{0.5\linewidth}{0.5pt} \\
    \vspace{0.5em}
    \footnotesize \textcolor{textlight}{\copyright\ 2026 StatBridge Studio — All rights reserved.}
\end{center}

\end{document}
